---
title: "Using linregpkg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using linregpkg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(linregpkg)
```

`linregpkg` fits a multiple linear regression using the QR decomposition of
the design matrix. The result is an object of class `linreg`, with methods for
printing and summarising the fit, extracting coefficients, residuals and
predicted values, and drawing diagnostic plots.

## Fit a model

We use the built-in `iris` dataset to model petal length as a function of
sepal width and sepal length:

```{r fit-model}
model <- linreg(
  Petal.Length ~ Sepal.Width + Sepal.Length,
  data = iris
)
```

The function takes exactly two arguments: a formula and a data frame. It
returns the estimates and model statistics in a `linreg` object.

## Print the fitted coefficients

`print()` displays the model call and named coefficient estimates:

```{r print-model}
print(model)
```

## Extract coefficients

`coef()` returns the estimates as a named numeric vector:

```{r coefficients}
coef(model)
```

## Inspect residuals and predictions

`resid()` returns the residuals, while `pred()` returns the fitted values:

```{r residuals-and-predictions}
head(resid(model))
head(pred(model))
```

The standard `residuals()` generic is also supported:

```{r residuals-generic}
head(residuals(model))
```

## Summarise the fit

`summary()` reports coefficient estimates, standard errors, t-values and
p-values, followed by the residual standard error and residual degrees of
freedom:

```{r model-summary}
summary(model)
```

## Diagnostic plots

`plot()` draws Residuals vs Fitted and Scale-Location diagnostic plots using
`ggplot2`:

```{r diagnostic-plots, fig.width=7, fig.height=5}
plot(model)
```
